R Notebook

### 2022-09-12 Step4_PredAccSAaxis/SA_rank_by_PFN_spins.Rmd
z-scored S-A axis ranks for viz

df.acc.SA <- cbind.data.frame(predacc_PC1,predacc_PC2,predacc_PC3,SArank_byPFN)

#ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC1)) + geom_bar(stat="identity",fill=SArank_byPFN)

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC1acc.png",
    width = 4000, 
    height = 4000,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC1,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 30000) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy (General Cognition)")
dev.off()

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC2acc.png",
    width = 4000, 
    height = 4000,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC2,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 30000) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy (Executive Function)")
dev.off()

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC3acc.png",
    width = 4000, 
    height = 4000,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC3,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 30000) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy (Learning/Memory)")
dev.off()

@@

# wider format figures for poster 
```{r}
png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC1acc_wide.png",
    width = 3000, 
    height = 2800,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC1,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 30000) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy")
dev.off()

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC2acc_wide.png",
    width = 3000, 
    height = 2800,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC2,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 30000) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy")
dev.off()

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC3acc_wide.png",
    width = 3000, 
    height = 2800,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC3,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 30000) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy")
dev.off()

>>>>

## Combine data frame and z-score the S-A axis ranks for visualization
df.acc.SA <- cbind.data.frame(predacc_PC1,predacc_PC2,predacc_PC3,SArank_byPFN)
df.acc.SA$SArank_byPFN <- (df.acc.SA$SArank_byPFN - mean(df.acc.SA$SArank_byPFN,na.rm=TRUE))/sd(df.acc.SA$SArank_byPFN,na.rm=TRUE)

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC1acc.png",
    width = 4000, 
    height = 4000,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC1,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 0) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy (General Cognition)")
dev.off()

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC2acc.png",
    width = 4000, 
    height = 4000,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC2,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 0) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy (Executive Function)")
dev.off()

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC3acc.png",
    width = 4000, 
    height = 4000,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC3,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 0) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy (Learning/Memory)")
dev.off()

@@

# wider format figures for poster 
```{r}
png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC1acc_wide.png",
    width = 3000, 
    height = 2800,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC1,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 0) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy")
dev.off()

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC2acc_wide.png",
    width = 3000, 
    height = 2800,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC2,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 0) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy")
dev.off()

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC3acc_wide.png",
    width = 3000, 
    height = 2800,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC3,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 0) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy")
dev.off()
